Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-02-15 hscc2017/paper.tex
comma

%------------------------------------
\subsection{Model Imprecision, Finite Word Length Representation, and Quantization Effects}
\label{verifying-closed-loop-control-systems}
%------------------------------------

@@

% \blue{
% This candidate solution is validated as the final solution by the next 
% {\sc verify} phase.
% }
%
\begin{figure}[htb]
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{figures/runningexample_bd0.pdf}
        \caption{Original controller~\cite{DBLP:conf/hybrid/WangGRJF16}}
        \label{fig:original}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{figures/runningexample_bd2.pdf}
        \caption{Controller synthesized by \tool}
        \label{fig:cegiscontroller}
    \end{subfigure}
    \caption{Bode diagram for original controller in~\cite{DBLP:conf/hybrid/WangGRJF16}, 
    and for newly synthesized closed-loop system}\label{fig:bode}
\end{figure}

>>>>

%------------------------------------
\subsection{Model Imprecision, Finite Word Length Representation and Quantization Effects}
\label{verifying-closed-loop-control-systems}
%------------------------------------

@@

% \blue{
% This candidate solution is validated as the final solution by the next 
% {\sc verify} phase.
% }
%
\begin{figure}[htb]
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{figures/runningexample_bd0.pdf}
        \caption{Original controller~\cite{DBLP:conf/hybrid/WangGRJF16}}
        \label{fig:original}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{figures/runningexample_bd2.pdf}
        \caption{Controller synthesized by \tool}
        \label{fig:cegiscontroller}
    \end{subfigure}
    \caption{Bode diagram for original controller in~\cite{DBLP:conf/hybrid/WangGRJF16} 
    and for newly synthesized closed-loop system}\label{fig:bode}
\end{figure}
